### 2011-06-15 Text/paper.tex
Some more results

The volumetric mass transfer coefficient is calculated according to the work of
\citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) at time
$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
coefficient is calculated as:
\begin{equation}
\label{main:simulation:equation}
k_L a=\frac{\text{Flux}}{C_s-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell volume}},
\end{equation}
where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. To properly do
non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
inside the lattice Botlzmann system. The time conversion can be easily obtained:
\begin{equation}
\begin{aligned}
U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
\Delta t=1.5\,\mathrm{mm} \frac{0.0559}{0.902\,\mathrm{m/s}}=9.3\times 10^{-5}\,\mathrm{s} 
\end{aligned}
\end{equation}

@@

\section{Simulation results}

\subsection{Bubble velocity dependence}
After calculation of the results and using Eq.\ref{main:simulation:equation} One can see the mass
transfer coefficients indicated in Fig. \ref{}.

>>>>

The volumetric mass transfer coefficient is calculated according to the work of
\citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) 
{\color{red} (In this particular moment I don't know whether to take the Volume of whole domain or
just the liquid phase. I will go for whole domain.)}
at time
$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
coefficient is calculated as:
\begin{equation}
\label{main:simulation:equation}
k_L a=\frac{\text{Flux}}{C_s-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell volume}},
\end{equation}
where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
{\color{red} Do not understand why we need this ratio bubble surface area/unit cell volume. In this
case the dimensional units do not coincide. In the calculations I will avoid it until further
clearance.}
To properly do
non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
inside the lattice Botlzmann system. The time conversion can be easily obtained:
\begin{equation}
\begin{aligned}
&U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
&\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
&\Delta t=\frac{1.5\,\mathrm{mm}}{200} \frac{0.0559}{0.902\,\mathrm{m/s}}=4.64\times
10^{-7}\,\mathrm{s} 
\end{aligned}
\end{equation}

@@

\section{Simulation results}
\subsection{Steady-state}
Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
a steady-state condition the average of  
\begin{figure}
\includegraphics[width=\textwidth]{Figures/steady_state.eps}
\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
state can be reached after $500000$. The mass transfer coefficient is taken as the average from
$500000$ to $1000000$.\label{fig:steady:state}}
\end{figure}
